\paragraph*{Claim}

The concept class $\mathcal{C}=\left\{ x\in\mathbb{R}^{2}\mid a\leq x_{1}\leq b,\, c\leq x_{2}\leq d\right\} $
consisting of all axis parallel (aligned) rectangles is polynomially
PAC-learnable.


\paragraph*{Proof}

By corollary 1 of slide 12 of lecture 2014-12-19, a concept class
$\text{\ensuremath{\mathcal{C}}}$ is polynomially PAC-learnable if 
\begin{enumerate}
\item the VC-dimension of $\mathcal{C}$ is bounded by polynomial of the
parameters of $\mathcal{C}$, and
\item the problem of finding a hypothesis consistent with a sample $S$
can be solved in time polynomial in $\vert S\vert$ and the parameters
of $\mathcal{C}$.
\end{enumerate}
Show (1):

To show that $\mathrm{VC_{dim}}(\mathcal{C})\geq4$, consider the points
$\{(1,0),(0,1),(-1,0),(0,-1)\}$ on the unit circle. This set can
be shattered by $\mathcal{C}$. All four points are realized by $\left\{ x\in\mathbb{R}^{2}\mid-m\leq x_{1}\leq m,\,-m\leq x_{2}\leq m\right\} $
and the empty set is realized by $\left\{ x\in\mathbb{R}^{2}\mid-m\leq x_{1}\leq m,\,-m\leq x_{2}\leq m\right\} $
for some $m\geq1$ and some $m<1$, respectivley. Single points $y$
(and thus also three points) are realized by $\left\{ x\in\mathbb{R}^{2}\mid y_{1}-\epsilon\leq x_{1}\leq y_{1}+\epsilon,\, y_{2}-\epsilon\leq x_{2}\leq y_{2}+\epsilon\right\} $
for some $\epsilon<1$. The case of two adjacent points can be realized
by unit squares with a vertex in the origin. The case of two points
on the same coordinate axis can be realized by rectangles of sufficiently
large extent along the corresponding coordinate axis and sufficiently
small extent along the perpendicular axis.

Five and more points can not be shattered by $\mathcal{C}$. If the
convex hull of five points form a quadrilateral (or a polygon with
less than four vertices), it is not possible to realize the set of
the quadrilateral vertices without the point in the interior (or the
point on an edge if the remaining point is not in the interior) because
the rectangles in $\mathcal{C}$ are convex. If the convex hull of
five points forms a pentagon, one may try to realize single points
by starting with a sufficiently large rectangle to realize all points.
Thereafter, the rectangle is scaled from one edge until a vertex of
the pentagon is not realized anymore. Since the rectangle only has
four edges, it is impossible to do this procedure individually for
all five vertices of a pentagon.

Show (2):

Such an algorithm is given by the FIND\_S algorithm:
\begin{enumerate}
\item Initialize concept $c=\left\{ x\in\mathbb{R}^{2}\mid\infty\leq x_{1}\leq-\infty,\,\infty\leq x_{2}\leq-\infty\right\} $.
\item For all positive training examples $x\in S$ do:

\begin{enumerate}
\item If $x\in c$, do nothing.
\item Otherwise, shift $(a,b,c,d)$ of $c=\left\{ x\in\mathbb{R}^{2}\mid a\leq x_{1}\leq b,\, c\leq x_{2}\leq d\right\} $
by the least possible amount to $(a',b',c',d')$ such that 
\[
x\in\left\{ x\in\mathbb{R}^{2}\mid a'\leq x_{1}\leq b',\, c'\leq x_{2}\leq d'\right\} .
\]
Update $c=\left\{ x\in\mathbb{R}^{2}\mid a'\leq x_{1}\leq b',\, c'\leq x_{2}\leq d'\right\} $.
\end{enumerate}
\item Return $c$.
\end{enumerate}
This algorithm is time constant in the parameter of $\mathcal{C}$
and time linear in $\vert S\vert$.\newline \phantom{x}\hfill $\square$